\chapter{Future Work}\label{ch:future}

The question of interest is whether there exist Lagrangian cobordisms from the unknot to all Legendrian ribbon knots. It suffices in this case to show that this is true for all nonstabilized representatives. The representatives with maximal $\tb$ are a subset of the nonstabilized representatives.
In this paper we showed that there exist Lagrangian cobordisms from the unknot to \emph{at least one} representative with maximal $\tb$ for a large family of ribbon pretzel knots, but our solution does not give information about the answer to this question in general. 

Our solution made use of a parameterization of ribbon pretzel knots, and we computed the maximal $\tb$ using an explicit formula for the Kauffman bound. There is another class of ribbon knots for which this approach might work --- 2-bridge knots.
The Kauffman bound is known to be sharp for these knots \cite{ng}, and an algorithm exists for computing it \cite{luzhong-2bridge}, much like the algorithm we used for pretzel knots.
Moreover, many of the prime knots for which we have failed to explicitly find maximal-$\tb$ cobordisms from the unknot are 2-bridge: for example, $8_8$ and $8_9$. In fact, there are several known families of 2-bridge ribbon knots, and it is conjectured that these families include all 2-bridge ribbon knots \cite{lamm}.

Yet in the case of the pretzel knots $P(3, -3, n)$, our proof relied on an explicit stabilized unknot for each $n$ such that each cobordism could be constructed using the exact same sequence of moves.
If a similar method could be used to prove the existence of such cobordisms for 2-bridge knots, the first step would be to find a single explicit example --- which so far we have failed to do.

However, finding a positive answer in general is much more difficult due to the wide variety of ways that the equivalence classes of Legendrian knots can be organized. For example, Menasco and LaFountain give an example of a knot having \emph{nonstabilized} representatives with the same $\tb$ and rotation number as stabilized representatives \cite{mountain}. There exist knots with infinitely many pairs of distinct Legendrian representatives $(K, K')$ such that $\tb K = \tb K'$ and $\rot K = \rot K'$ (in particular, this is true of $P_{-4}$). More examples of the strangeness of Legendrian equivalence classes may be readily found in \cite{atlas}. Yet the takeaway is that the nonstabilized Legendrian representatives of a topological knot type can have little in common, making it difficult to to prove anything about them.


